\vskip-0.6in \Large Political Uncertainty

### 2015-03-27 GS-extension.tex
fix typo on line 153
add new section on 3-legislator (discrete) model

							\item Maximizing the total probability mass where $v(j) \geq 0$?

@@

>>>>

							\item Maximizing the total probability mass where $v(j) \leq 0$?

@@

\newpage
Discrete version (Conversation between Kristy and Frank, 3/27/15)
\begin{itemize}
	\item Purpose: try to understand what the right objective function is. Does maximizing total probability also maximize the probability of winning?
		\begin{itemize}
			\item Note that this model \textit{may} introduce interdependence between the bid functions that does not exist in the continuous model
			\item What is not clear is whether this happens when the WTP constraint is not binding, which I'm going to assume from the start, and maybe impose later
		\end{itemize}
	\item Frank prefers to write
	  \[
		  v(z) = \alpha -\beta z + \ve_z + a(z) - b(z)
		\]
			\begin{itemize}
				\item Note that, in a probit we will have to worry about separately identifying the parameters. So for now, will assume $\ve$ does not vary in $z$
				\item Also going to ignore Vote Buyer A's choice for now, so we have
			\end{itemize}
	  \[
		  v(z) = \alpha -\beta z + \ve - b(z)
		\]
	\item Then the probability that legislator $z$ votes against the new proposal is
	  \[
		  \Pr\left[v(z)\leq 0 \right] = \Pr\left[\alpha -\beta z + \ve - b(z) \leq 0 \right] 
			                            = \Pr\left[\ve \leq \beta z - \alpha + b(z) \right] 
		\]
		Assuming $\ve \sim N(0,1)$, the probability that legislator $z$ votes ``no'' is $\Phi\left(\beta z - \alpha + b(z) \right)$
	\item Take a model with three legislators with ideal points at $z=-\frac{1}{2}$, $z=0$ and $z=\frac{1}{2}$. Then the three probabilities are
		\begin{itemize}
			\item $\Phi\left(-\frac{\beta}{2} - \alpha + b(z) \right)$, $\Phi\left(- \alpha + b(z) \right)$, and $\Phi\left(\frac{\beta}{2} - \alpha + b(z) \right)$
			\item Whether a legislator $z$ votes ``no'' is a random variable, denote it $X(z)$, distributed Bernoulli with this probability:
				\[
				  X(z) \sim \text{Bernoulli}(p(z)) \hskip.2in \text{where} \hskip.2in p(z) = \Phi\left(\beta z - \alpha + b(z) \right)
				\]
			\item Need to max probability of at least two voting ``no'': $\Pr(S \geq 2)$ where $S = X\left(-\frac{1}{2}\right) + X\left(0\right) + X\left(\frac{1}{2}\right)$
			\item Thus, maximization problem for Vote Buyer B (in absence of Vote Buyer A) is
			  \[
			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} \Pr(X\left(-\frac{1}{2}\right)=1)\Pr(X\left(0\right)=1)\Pr(X\left(\frac{1}{2}\right)=0)  + ...
				\]
		\end{itemize}
\end{itemize}
